

```{r,  echo=FALSE, include=FALSE}

country<-unique(dataglobal$Country)[i]
datacountry<-dataglobal[dataglobal$Country==country,]
datacountrybyspec<-databyspecimen[databyspecimen$Country==country,]

```

## Summary `r country`

In `r country`, `r length(unique(datacountry$Specimen.code))` animals were sampled, from `r length(unique(datacountry$specimen.latin.name))` species.
 
These specimen are distributed between the different types of surveillance activities and species as follow:

```{r, echo=FALSE, results='asis',message=FALSE,warning=FALSE}
library(knitr)

kable(cbind(table(as.character(datacountrybyspec$specimen.projects)),prop.table(table(as.character(datacountrybyspec$specimen.projects)))), caption="Specimen by project",col.names = c("Number of specimen","Proportion"))
```
 
 
```{r, echo=FALSE, results='asis',message=FALSE,warning=FALSE}
library(knitr)


kable(cbind(table(as.character(datacountrybyspec$specimen.common.name)),prop.table(table(as.character(datacountrybyspec$specimen.common.name)))), caption="Specimen by species",col.names = c("Number of specimen","Proportion"))


```

The distribution of cases across `r country` is illustrated on this map of recently submitted specimen:

```{r echo=FALSE, message=FALSE, warning=FALSE}
#library(leaflet)
##library(mapview)
#library(png)
#mymap<-datacambodia[,c("Latitude","Longitude")] %>%
#  leaflet()%>%
#  addTiles()%>%
#  addCircleMarkers()
#print(mymap)
#mapshot(mymap,file="C:/Users/mpruvot/Documents/Work/WCS/DTRA/Reporting/Jan 2020/mymap.png")
#img_path<-"C:/Users/mpruvot/Documents/Work/WCS/DTRA/Reporting/Jan 2020/mymap.png"
#readPNG(img_path,native=T,info=T)

library(ggmap)
myMap <- get_map(location = c(left = round(min(datacountrybyspec$Longitude),0)-1,
                                    bottom = round(min(datacountrybyspec$Latitude),0)-1,
                                    right = round(max(datacountrybyspec$Longitude),0)+1,
                                    top = round(max(datacountrybyspec$Latitude),0)+1),
          maptype = "hybrid",
          crop = FALSE,
          zoom = 7)
# plot map

ggmap(myMap)+
  geom_point(data=datacountrybyspec,aes(x=Longitude,y=Latitude, color="red",alpha=0.2),size=5, shape=19)+
  guides(color = FALSE, alpha = FALSE, size = FALSE)
```

Total number of samples:
```{r ,echo=FALSE}
library(stringr)
cat(nrow(datacountry))

```


