---
title: "Report January 2020"
output: word_document
params: 
  datain: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

dataglobal<-read.csv(file=input$datain$datapath)
databyspecimen<-dataglobal %>% group_by(Specimen.code) %>% filter(row_number()==1) %>% as.data.frame()

```

# Summary across `r length(unique(dataglobal$Country))` countries

Since the beginning of the surveillance efforts under the DTRA INDOPACOM Wildlife Biosurveillance project, `r length(unique(dataglobal$Specimen.code))` animals were sampled, from `r length(unique(dataglobal$specimen.latin.name))` species, in `r length(unique(dataglobal$Country))` countries.

```{r echo=FALSE, results='asis',message=FALSE,warning=FALSE}
library(plotrix)
bycountry<-as.data.frame(table(databyspecimen$Country))
bycountry$Var1<-as.character(bycountry$Var1)
pie3D(bycountry$Freq,labels=bycountry$Var1,radius=1, col = c("#999999", "#E69F00", "#56B4E9"),explode=0.2,theta=pi/3,start = pi/5)
```

# Summary by country

```{r  include=FALSE,echo=FALSE,message=FALSE,results="asis",warning=FALSE}
out<-NULL
for (i in 1:length(unique(dataglobal$Country))){
  out<-c(out,knitr::knit_child('test4_countrygeneric.Rmd'))
}

```
`r paste(out, collapse='\n')`



## Performance indicators

```{r  include=FALSE,echo=FALSE,message=FALSE,results="asis",warning=FALSE}
out2<-NULL
for (i in 1:length(unique(dataglobal$Country))){
  out2<-c(out2,knitr::knit_child('test4_perfindic_generic.Rmd'))
}


```
`r paste(out2, collapse='\n')`
